Principled Drug-Drug Interaction Terms for Bayesian Logistic Regression Models of Drug Safety in Oncology Phase I Combination Trials

### 2023-02-24 manuscript.tex
* Add data and code availability statement

>>>>

\section*{Data and Code availability}
The source LaTeX code for this manuscript as well as the R source code that fits the various models, produces the figures and compiles the manuscript are available in the supplementary material of this article, as well as on the \textbf{Git repository} at \url{https://github.com/luwidmer/ddi-manuscript}.
